### 2018-04-03 paper/user-model.tex
new subsubsection
Changes [Ff]igure~\ref to \[Cc]ref

In figure~\ref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
The represented user possesses a phone, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.

@@

Figure~\ref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
Each device starts offline; the user can toggle one device per round (or do nothing).
In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
As a consequence, several devices can be online at the same time, as happens in the figure.

>>>>

In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
The represented user possesses a phone, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.

@@

\Cref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
Each device starts offline; the user can toggle one device per round (or do nothing).
In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
As a consequence, several devices can be online at the same time, as happens in the figure.
